Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-18 paper/main.tex
update table

%\begin{table}
%  \caption{Results.\label{tab:results}}
%%\begin{adjustbox}
%\resizebox{\textwidth}{!}{%
%\begin{tabular}{lllrrrrrrr}
%\toprule
%{} & Problem &                instance &  Fitness\_CEGO\_mean &  Fitness\_CEGO\_std &  Fitness\_UMM\_mean &  Fitness\_UMM\_std &  Improvement &  ttest statistic &  ttest pvalue \\
%\midrule
%0  &     LOP &  lop/RandA1/N-t1d100.01 &            78696.6 &        811.368145 &           76119.6 &       915.392836 &     0.032746 &         6.662091 &  2.989433e-06 \\
%1  &     LOP &  lop/RandA1/N-t1d100.02 &            79686.5 &        367.876262 &           76827.7 &       890.969391 &     0.035876 &         9.378614 &  2.374606e-08 \\
%2  &     LOP &  lop/RandA1/N-t1d150.01 &           187605.5 &       1906.941953 &          179508.3 &      1647.878437 &     0.043161 &        10.159726 &  6.994357e-09 \\
%3  &     LOP &  lop/RandA1/N-t1d150.02 &           184320.9 &        973.457920 &          177592.8 &      1196.159298 &     0.036502 &        13.795848 &  5.183671e-11 \\
%4  &     LOP &  lop/RandA1/N-t1d200.01 &           335391.1 &       2288.960096 &          323513.6 &      1371.235712 &     0.035414 &        14.076557 &  3.714220e-11 \\
%5  &     LOP &  lop/RandA1/N-t1d200.02 &           333149.5 &       2497.207474 &          319675.8 &      2242.631629 &     0.040443 &        12.694417 &  2.029610e-10 \\
%6  &     LOP &  lop/RandA2/N-t2d150.01 &            24682.7 &        976.639596 &           15297.7 &       563.527787 &     0.380226 &        26.320561 &  8.038269e-16 \\
%7  &     LOP &  lop/RandA2/N-t2d150.02 &            24250.8 &       1354.897110 &           14724.9 &       667.454276 &     0.392808 &        19.944373 &  1.010663e-13 \\
%8  &    PFSP &          pfsp/rec05.txt &             1317.9 &         25.075220 &            1330.7 &        17.901272 &    -0.009712 &        -1.313790 &  2.054160e-01 \\
%9  &    PFSP &          pfsp/rec13.txt &             2128.2 &         24.965754 &            2158.7 &        29.533597 &    -0.014331 &        -2.494040 &  2.258601e-02 \\
%10 &    PFSP &          pfsp/rec19.txt &             2398.6 &         19.839355 &            2405.1 &        12.582616 &    -0.002710 &        -0.874932 &  3.931359e-01 \\
%11 &     QAP &           qap/kra32.dat &           115907.0 &       4663.427566 &          116320.0 &      4673.468852 &    -0.003563 &        -0.197816 &  8.454055e-01 \\
%12 &     QAP &           qap/nug12.dat &              624.2 &         26.288147 &             660.4 &        17.276831 &    -0.057994 &        -3.639054 &  1.876810e-03 \\
%13 &     QAP &           qap/nug30.dat &             7486.8 &         40.411220 &            7474.0 &        83.910005 &     0.001710 &         0.434612 &  6.690098e-01 \\
%14 &     QAP &           qap/tho30.dat &           192416.0 &       2584.174401 &          191482.0 &      4419.722264 &     0.004854 &         0.576896 &  5.711548e-01 \\
%\bottomrule
%\end{tabular}}
%% \end{adjustbox}
% \end{table}

\resizebox{\textwidth}{!}{%
\begin{tabular}{llllllrrr}
\toprule
{} & Problem &     Instance &        UMM fitness &       CEGO fitness &                        Confidence interval &  UMM Runtime &  CEGO Runtime &  CEGO F. evaluations \\
\midrule
0  &     LOP &  N-t1d100.01 &    76119.6 (915.4) &    78696.6 (811.4) &   (1763.4904574743996, 3390.5095425256004) &      11436.2 &      260954.5 &                111.8 \\
1  &     LOP &  N-t1d100.02 &    76827.7 (891.0) &    79686.5 (367.9) &    (2194.5410893080507, 3523.058910691955) &      11353.3 &      262421.6 &                110.7 \\
2  &     LOP &  N-t1d150.01 &  179508.3 (1647.9) &  187605.5 (1906.9) &     (6420.259663264915, 9774.140336735109) &      23395.6 &      261712.4 &                 73.9 \\
3  &     LOP &  N-t1d150.02 &  177592.8 (1196.2) &   184320.9 (973.5) &     (5700.461476832616, 7755.738523167395) &      23361.2 &      263389.9 &                 74.1 \\
4  &     LOP &  N-t1d200.01 &  323513.6 (1371.2) &  335391.1 (2289.0) &     (10076.07401989604, 13678.92598010396) &      38476.8 &      263467.5 &                 55.6 \\
5  &     LOP &  N-t1d200.02 &  319675.8 (2242.6) &  333149.5 (2497.2) &   (11241.971680405779, 15705.428319594244) &      38268.3 &      265217.5 &                 56.5 \\
6  &     LOP &  N-t2d150.01 &    15297.7 (563.5) &    24682.7 (976.6) &    (8622.206776092156, 10147.793223907844) &      25318.6 &      262324.3 &                 74.6 \\
7  &     LOP &  N-t2d150.02 &    14724.9 (667.5) &   24250.8 (1354.9) &    (8495.057408450935, 10556.742591549064) &      25425.6 &      262079.2 &                 74.8 \\
8  &     LOP &  N-t2d200.01 &   33465.2 (2001.0) &   57098.6 (4452.8) &   (20284.508914101127, 26982.291085898876) &      40340.9 &      263908.9 &                 56.3 \\
9  &     LOP &  N-t2d200.02 &   35901.8 (2077.5) &   58123.0 (2334.9) &     (9515.181030361815, 34927.21896963818) &      40153.1 &      261723.6 &                 55.0 \\
10 &    PFSP &    rec05.txt &      1330.7 (17.9) &      1317.9 (25.1) &  (-33.424760001214985, 7.8247600012150755) &        506.1 &      139893.0 &                400.0 \\
11 &    PFSP &    rec13.txt &      2158.7 (29.5) &      2128.2 (25.0) &   (-56.24362499249925, -4.756375007500754) &        506.8 &      140167.2 &                400.0 \\
12 &    PFSP &    rec19.txt &      2405.1 (12.6) &      2398.6 (19.8) &   (-22.313869704790818, 9.313869704790818) &       1078.3 &      295442.7 &                400.0 \\
13 &     QAP &    kra32.dat &  116320.0 (4673.5) &  115907.0 (4663.4) &    (-4799.295389697205, 3973.295389697205) &       1194.8 &      344766.2 &                400.0 \\
14 &     QAP &    nug12.dat &       660.4 (17.3) &       624.2 (26.3) &  (-57.337505259978144, -15.06249474002172) &        180.0 &       53149.3 &                400.0 \\
15 &     QAP &    nug30.dat &      7474.0 (83.9) &      7486.8 (40.4) &     (-50.84533806724974, 76.4453380672501) &       1073.5 &      303352.6 &                400.0 \\
16 &     QAP &    tho30.dat &  191482.0 (4419.7) &  192416.0 (2584.2) &   (-2527.0213832396516, 4395.021383239651) &       1066.5 &      306451.3 &                400.0 \\
\bottomrule
\end{tabular}
}

>>>>

%%\begin{adjustbox}
%\resizebox{\textwidth}{!}{%
%\begin{tabular}{lllrrrrrrr}
%\toprule
%{} & Problem &                instance &  Fitness\_CEGO\_mean &  Fitness\_CEGO\_std &  Fitness\_UMM\_mean &  Fitness\_UMM\_std &  Improvement &  ttest statistic &  ttest pvalue \\
%\midrule
%0  &     LOP &  lop/RandA1/N-t1d100.01 &            78696.6 &        811.368145 &           76119.6 &       915.392836 &     0.032746 &         6.662091 &  2.989433e-06 \\
%1  &     LOP &  lop/RandA1/N-t1d100.02 &            79686.5 &        367.876262 &           76827.7 &       890.969391 &     0.035876 &         9.378614 &  2.374606e-08 \\
%2  &     LOP &  lop/RandA1/N-t1d150.01 &           187605.5 &       1906.941953 &          179508.3 &      1647.878437 &     0.043161 &        10.159726 &  6.994357e-09 \\
%3  &     LOP &  lop/RandA1/N-t1d150.02 &           184320.9 &        973.457920 &          177592.8 &      1196.159298 &     0.036502 &        13.795848 &  5.183671e-11 \\
%4  &     LOP &  lop/RandA1/N-t1d200.01 &           335391.1 &       2288.960096 &          323513.6 &      1371.235712 &     0.035414 &        14.076557 &  3.714220e-11 \\
%5  &     LOP &  lop/RandA1/N-t1d200.02 &           333149.5 &       2497.207474 &          319675.8 &      2242.631629 &     0.040443 &        12.694417 &  2.029610e-10 \\
%6  &     LOP &  lop/RandA2/N-t2d150.01 &            24682.7 &        976.639596 &           15297.7 &       563.527787 &     0.380226 &        26.320561 &  8.038269e-16 \\
%7  &     LOP &  lop/RandA2/N-t2d150.02 &            24250.8 &       1354.897110 &           14724.9 &       667.454276 &     0.392808 &        19.944373 &  1.010663e-13 \\
%8  &    PFSP &          pfsp/rec05.txt &             1317.9 &         25.075220 &            1330.7 &        17.901272 &    -0.009712 &        -1.313790 &  2.054160e-01 \\
%9  &    PFSP &          pfsp/rec13.txt &             2128.2 &         24.965754 &            2158.7 &        29.533597 &    -0.014331 &        -2.494040 &  2.258601e-02 \\
%10 &    PFSP &          pfsp/rec19.txt &             2398.6 &         19.839355 &            2405.1 &        12.582616 &    -0.002710 &        -0.874932 &  3.931359e-01 \\
%11 &     QAP &           qap/kra32.dat &           115907.0 &       4663.427566 &          116320.0 &      4673.468852 &    -0.003563 &        -0.197816 &  8.454055e-01 \\
%12 &     QAP &           qap/nug12.dat &              624.2 &         26.288147 &             660.4 &        17.276831 &    -0.057994 &        -3.639054 &  1.876810e-03 \\
%13 &     QAP &           qap/nug30.dat &             7486.8 &         40.411220 &            7474.0 &        83.910005 &     0.001710 &         0.434612 &  6.690098e-01 \\
%14 &     QAP &           qap/tho30.dat &           192416.0 &       2584.174401 &          191482.0 &      4419.722264 &     0.004854 &         0.576896 &  5.711548e-01 \\
%\bottomrule
%\end{tabular}}
%% \end{adjustbox}
% \end{table}

    \newcommand{\mcolc}[2]{\multicolumn{#1}{c}{\bf #2}}
\begin{table}
  \caption{Results.\label{tab:results}}
  \resizebox{\textwidth}{!}{%
\begin{tabular}{*{6}{r}c*{3}{r}}
  \toprule
            &                  & \mcolc{4}{Mean fitness (sd)} &                 & \mcolc{2}{Mean runtime}             & \bf     Mean FE\\\cmidrule{3-6}\cmidrule(lr){8-9}
\bf Problem & \bf     Instance & \mcolc{2}{UMM}               & \mcolc{2}{CEGO} & \bf 95\% CI for the mean difference & \bf UMM  & \bf CEGO                                  & \bf CEGO           \\\midrule
    LOP     & N-t1d100.01      & 76119.6                      & (915.4)         & 78696.6                             & (811.4)  & (1763.4904574743996, 3390.5095425256004)  & 11436.2 & 260954.5 & 111.8 \\
    LOP     & N-t1d100.02      & 76827.7                      & (891.0)         & 79686.5                             & (367.9)  & (2194.5410893080507, 3523.058910691955)   & 11353.3 & 262421.6 & 110.7 \\
    LOP     & N-t1d150.01      & 179508.3                     & (1647.9)        & 187605.5                            & (1906.9) & (6420.259663264915, 9774.140336735109)    & 23395.6 & 261712.4 & 73.9  \\
    LOP     & N-t1d150.02      & 177592.8                     & (1196.2)        & 184320.9                            & (973.5)  & (5700.461476832616, 7755.738523167395)    & 23361.2 & 263389.9 & 74.1  \\
    LOP     & N-t1d200.01      & 323513.6                     & (1371.2)        & 335391.1                            & (2289.0) & (10076.07401989604, 13678.92598010396)    & 38476.8 & 263467.5 & 55.6  \\
    LOP     & N-t1d200.02      & 319675.8                     & (2242.6)        & 333149.5                            & (2497.2) & (11241.971680405779, 15705.428319594244)  & 38268.3 & 265217.5 & 56.5  \\
    LOP     & N-t2d150.01      & 15297.7                      & (563.5)         & 24682.7                             & (976.6)  & (8622.206776092156, 10147.793223907844)   & 25318.6 & 262324.3 & 74.6  \\
    LOP     & N-t2d150.02      & 14724.9                      & (667.5)         & 24250.8                             & (1354.9) & (8495.057408450935, 10556.742591549064)   & 25425.6 & 262079.2 & 74.8  \\
    LOP     & N-t2d200.01      & 33465.2                      & (2001.0)        & 57098.6                             & (4452.8) & (20284.508914101127, 26982.291085898876)  & 40340.9 & 263908.9 & 56.3  \\
    LOP     & N-t2d200.02      & 35901.8                      & (2077.5)        & 58123.0                             & (2334.9) & (9515.181030361815, 34927.21896963818)    & 40153.1 & 261723.6 & 55.0  \\\midrule
   PFSP     & rec05            & 1330.7                       & (17.9)          & 1317.9                              & (25.1)   & (-33.424760001214985, 7.8247600012150755) & 506.1   & 139893.0 & 400.0 \\
   PFSP     & rec13            & 2158.7                       & (29.5)          & 2128.2                              & (25.0)   & (-56.24362499249925, -4.756375007500754)  & 506.8   & 140167.2 & 400.0 \\
   PFSP     & rec19            & 2405.1                       & (12.6)          & 2398.6                              & (19.8)   & (-22.313869704790818, 9.313869704790818)  & 1078.3  & 295442.7 & 400.0 \\\midrule
    QAP     & kra32            & 116320.0                     & (4673.5)        & 115907.0                            & (4663.4) & (-4799.295389697205, 3973.295389697205)   & 1194.8  & 344766.2 & 400.0 \\
    QAP     & nug12            & 660.4                        & (17.3)          & 624.2                               & (26.3)   & (-57.337505259978144, -15.06249474002172) & 180.0   & 53149.3  & 400.0 \\
    QAP     & nug30            & 7474.0                       & (83.9)          & 7486.8                              & (40.4)   & (-50.84533806724974, 76.4453380672501)    & 1073.5  & 303352.6 & 400.0 \\
    QAP     & tho30            & 191482.0                     & (4419.7)        & 192416.0                            & (2584.2) & (-2527.0213832396516, 4395.021383239651)  & 1066.5  & 306451.3 & 400.0 \\
\bottomrule
\end{tabular}}
\end{table}
